### 2016-12-12 poster/poster.tex
slightly update outline/notes on poster

%% Box 3
\headerbox{What else?}{name=methods,column=1,row=0.69, span=1}{
\color{black}
}

@@

%% BOX 0
\headerbox{Search Results}{name=results,column=2,row=0, span=1}{
%\begin{center}
%\includegraphics[scale=.5]{graphics/searchResults.JPG}
%
%\end{center}
%\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}%\addtolength{\itemindent}{-5pt}
%\item Search for words or phrases in the document text
%\item Filter on frames to examine relationships between the language used and the frame evoked
%\item Search via the wordcloud, the search bar, or by clicking on frames in search results
%\end{itemize}
}

@@

%% BOX 2
\headerbox{How many GPUs should I buy?}{name=results,column=2,row=0.69, span=1}{
}

>>>>

%% Box 3
\headerbox{Development experience}{name=methods,column=1,row=0.69, span=1}{
\color{black}
Implementing stuff sucked/was great/was average
}

@@

%% BOX 0
\headerbox{Results}{name=results,column=2,row=0, span=1}{
\begin{itemize}
\item Time per epoch (for each system)
\item Time per batch
\item Most used function/ most resources consumed by (for each system)
\item Metrics for that function (possibly others that are shared?)
\item Time to create computation graph
\end{itemize}

}

@@

%% BOX 2
\headerbox{Conclusions and Recommendations}{name=results,column=2,row=0.69, span=1}{

}
